### 2017-05-17 Doc/classicthesis/Chapters/Chapter03.tex
objectives

\section{Project description}

>>>>

\section{Project objectives}

We will divide the project in various objectives, starting from the principal goal, dividing our work in different categories.

\paragraph{Idemix and the IoT}
We part from this main objective, integrating IBM's privacy preserving system in the IoT environment.

\paragraph{Analysis} Studying the state of the art for Idemix and the IoT, analyzing related projects like ABC4Trust's \ac{P2ABCE}, papers with similar approaches, and our task is to consider the best fitting solutions from where to start.

\paragraph{Design} After studying the existing works, we must give a formal solution to be implemented. This includes the theoretical architecture and steps to take, from the software to implement, to the hardware to use, and any simplifications to leave as future work.

Our \textbf{software} objectives include making it easily maintainable, structured and extensible, from the IoT and original project perspectives, that is, the IoT solution must be compatible with any non-IoT solutions, now and in the future with minimal effort, given new IoT systems or changes in the cryptographic protocols.

Our \textbf{hardware} objective is to use as constrained as possible devices, but taking in count how early in the project we are, that means, using now IoT devices that ease testing and development, having in mind for the future the other devices.

\paragraph{Validity and evaluation} Deploy in a \textbf{real scenario}, not simulators, a working \ac{PoC}, checking that it works as expected, and measuring its performance.
